Objective-first optimization for nanophotonics

### 2011-08-02 presentations/group-pres_2011-08-04.tex
Corrected wrong reference to matlab file on slide 15.
Changed figure source to public domain.

\BIT
\item need ability to \emph{incrementally} update the topology of the structure
\item describe $p$ using the \emph{interface} between the two materials
\item implicitly describe boundary using the \emph{level-set} of higher-dimensional function $\phi$
\begin{center}
\includegraphics[width=0.45\textwidth]{../figures/level-set.jpg} \\
source: \url{http://en.wikipedia.org/wiki/Level_set_method}
\end{center}
\EIT
\newpage

@@

\BIT
\item to test, hold $x$ constant, and update $p$ 
\begin{center}
\includegraphics[width=0.6\textwidth]{../figures/structure-progression.jpg} \\
\end{center}
\item code at \url{https://github.com/JesseLu/level-set} (\texttt{demo.m})
\item new code at \url{https://github.com/JesseLu/lset-opt}
\EIT

>>>>

\BIT
\item need ability to \emph{incrementally} update the topology of the structure
\item describe $p$ using the \emph{interface} between the two materials
\item implicitly describe boundary using the \emph{level-set} of higher-dimensional function $\phi$
\begin{center}
\includegraphics[width=0.45\textwidth]{../figures/level-set.jpg} \\
source: public domain
\end{center}
\EIT
\newpage

@@

\BIT
\item to test, hold $x$ constant, and update $p$ (iterations 0, 5, 10, 15, 20 shown)
\begin{center}
\includegraphics[width=0.5\textwidth]{../figures/structure-progression.jpg} \\
\end{center}
\item code at \url{https://github.com/JesseLu/level-set} (\texttt{demo\_indep\_levelset.m})
\item new code at \url{https://github.com/JesseLu/lset-opt}
\EIT
